Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
approach

\frame{
\frametitle{Our Approach}
\begin{itemize}
	\item
\end{itemize}
}

@@

\frame{
\frametitle{Progress}
\begin{itemize}
	\item
\end{itemize}
}

@@

@@

\frame{
\centerline{Thank you!}
}

>>>>

\frame{
\frametitle{Our Approach}
\begin{itemize}
	\item Hierarchical Architecture
	\begin{itemize}
		\item Controllers' view do not span the whole network, but only the 'underlying network'
		\item Each controller behaves as a giant openflow switch for parent controller (Network Aggregation)
		\item Controller translates OFP commands and network updates between parent controller and underlying networks
	\end{itemize}
	\item Network Aggregation
	\begin{itemize}
		\item Share a condensed view of the network: A Network flow table
		\item Surpress network events such that aggregated network does not change: Reduce communication overhead
		\item Convert flow addtion/removal commands on aggregated network to actual network in an efficient way
	\end{itemize}
	\item Timestamp: 
		\item Handle domain level inconsistencies in "SDN Datapath" (Domain Network)
		\item Each domain i maintains a vector timestamp T_i[1...n] 
		\item (Routers in) A Domain may change flow depending on their timestamps
	\end{itemize}   
\end{itemize}
}

@@

\frame{
\frametitle{Network Aggregation}
\begin{itemize}
	\item
\end{itemize}
}

\frame{
\frametitle{Timestamp}
\begin{itemize}
	\item
\end{itemize}
}

@@

\section{What next ?}

@@

\frame{
	\frametitle{Hiccups}

\frame{
\centerline{Thank you!}
Suggestions and Questions are welcome, suggestions a little more than questions
}
